Homeless Shelter Usage Trends and Mortality: A Correlation Analysis

### 2024-04-15 paper/paper.qmd
made some graphs

library(tidyverse)
library(palmerpenguins)
```

@@

# consider using logistic regression -> usage patterns (independent variables) and mortality (dependent variable).
```

@@

# Results

>>>>

# load libraries
library(tidyverse)
library(here)
library(ggplot2)

# read in cleaned data
cleaned_data = read.csv(file=here("data/clean_data/cleaned_data.csv"))
```

@@

# THIS IS TEMPORARILY HERE -- POISSON MODEL GRAPH
#predicted_counts <- predict(poisson_model, type = "response")

# Create a scatter plot of observed vs. predicted counts
#plot(cleaned_data$Returned.to.shelter, cleaned_data$Deaths, 
#     xlab = "Returned to shelter", ylab = "Deaths",
#     main = "Observed vs. Predicted Counts",
#     pch = 16, col = "blue")
#lines(cleaned_data$Returned.to.shelter, predicted_counts, col = "red", type = "l", lwd = 2)
#legend("topright", legend = c("Observed", "Predicted"), 
#       col = c("blue", "red"), pch = c(16, NA), lty = c(NA, 1), lwd = #c(NA, 2))
```

@@

# Results
```{r graph1, fig.cap="temp"}
#| echo: false
#| warning: false
#| message: false
#| label: fig-1

# graph monthly homeless deaths over 2018 - 2022

# Convert Month.Year to factor to preserve the order of months
cleaned_data$Month.Year <- factor(cleaned_data$Month.Year, levels = unique(cleaned_data$Month.Year))

ggplot(cleaned_data, aes(x = Month.Year, y = Deaths)) +
  geom_line(aes(group = 1), color = "red", size = 1) +
  labs(x = "Month/Year", y = "Deaths", title = "Monthly Homeless Deaths") +
  scale_x_discrete(breaks = cleaned_data$Month.Year[seq(1, length(cleaned_data$Month.Year), by = 6)]) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
@fig-1 says this that and whatever.

```{r graph2, fig.cap="temp2"}
#| echo: false
#| warning: false
#| message: false
#| label: fig-2

# graph monthly returns to shelters over 2018 - 2022

# Convert Month.Year to factor to preserve the order of months
cleaned_data$Month.Year <- factor(cleaned_data$Month.Year, levels = unique(cleaned_data$Month.Year))

ggplot(cleaned_data, aes(x = Month.Year, y = Returned.to.shelter)) +
  geom_line(aes(group = 1), color = "blue", size = 1) +
  labs(x = "Month/Year", y = "Returns to Homeless Shelters", title = "Monthly Returns to Homeless Shelters") +
  scale_x_discrete(breaks = cleaned_data$Month.Year[seq(1, length(cleaned_data$Month.Year), by = 6)]) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@fig-2 says some stuff, other stuff and also stuff
